Structural Divergence Analysis

### 2017-05-10 analysis-dynamical-nH.Rmd
charla 11-5-17

```{r set-experimental-protein-names, comment = ""}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```
```{r prepare-mode-data}
# prepare the data
nH.exp = read.csv(nH.exp.fname, header = T)
nH.mut = read.csv(nH.mut.fname, header = T)
nH.medium = read.csv(nH.medium.fname, header = T)
```
### Dynamical divergence along normal modes

In this section we consider dynamical divergence using normal modes coordinates. We calculated <nH> and we z-normalized profiles.

```{r comparison-of-means, fig.cap = "blue = experimental - green = no-selection - red = selection"}
# calculate means
mean.nH.exp = colMeans(nH.exp, na.rm = T)
mean.nH.mut = colMeans(nH.mut)
mean.nH.medium = colMeans(nH.medium)

# scale profiles
mean.nH.exp = vscale(mean.nH.exp[which(!is.na(mean.nH.exp))])
mean.nH.mut = vscale(mean.nH.mut[which(!is.na(mean.nH.mut))])
mean.nH.medium = vscale(mean.nH.medium[which(!is.na(mean.nH.medium))])

plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

```{r vs-mean-plots}

# plot comparative profiles 
par(pty = "s")

plot(x = mean.nH.exp, 
     y = mean.nH.mut, 
     xlab = "<z.nH> experimental", 
     ylab = "<z.nH> no-selection")
abline(0, 1)

plot(x = mean.nH.exp, 
     y = mean.nH.medium, 
     xlab = "<z.nH> experimental", 
     ylab = "<z.nH> selection")
abline(0, 1)

plot(x = mean.nH.mut, 
     y = mean.nH.medium, 
     xlab = "<z.nH> no-selection", 
     ylab = "<z.nH> selection")
abline(0, 1)
```

```{r comparison-of-means-100-modes}

# get first 100 modes and re-scale
mean.nH.exp = vscale(mean.nH.exp[1:100])
mean.nH.mut = vscale(mean.nH.mut[1:100])
mean.nH.medium = vscale(mean.nH.medium[1:100])

plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

@@

# plot comparative profiles 
plot(x = mean.nH.exp, 
     y = mean.nH.mut, 
     xlab = "<z.nH> experimental", 
     ylab = "<z.nH> no-selection")
abline(0, 1)

plot(x = mean.nH.exp, 
     y = mean.nH.medium, 
     xlab = "<z.nH> experimental", 
     ylab = "<z.nH> selection")
abline(0, 1)

plot(x = mean.nH.mut, 
     y = mean.nH.medium, 
     xlab = "<z.nH> no-selection", 
     ylab = "<z.nH> selection")
abline(0, 1)
```
```{r comparison-of-means-20-modes}

# get first 100 modes and re-scale
mean.nH.exp = vscale(mean.nH.exp[1:20])
mean.nH.mut = vscale(mean.nH.mut[1:20])
mean.nH.medium = vscale(mean.nH.medium[1:20])

plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

```{r vs-mean-plots-20-modes}

# plot comparative profiles 
plot(x = mean.nH.exp, 
     y = mean.nH.mut, 
     xlab = "<z.nH> experimental", 
     ylab = "<z.nH> no-selection")
abline(0, 1)

plot(x = mean.nH.exp, 
     y = mean.nH.medium, 
     xlab = "<z.nH> experimental", 
     ylab = "<z.nH> selection")
abline(0, 1)

plot(x = mean.nH.mut, 
     y = mean.nH.medium, 
     xlab = "<z.nH> no-selection", 
     ylab = "<z.nH> selection")
abline(0, 1)
```

>>>>

```{r set-experimental-protein-names, comment = ""}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```
```{r prepare-mode-data}

# prepare the data
nH.exp = read.csv(nH.exp.fname, header = T)
rownames(nH.exp) = paste("mut", rownames(nH.exp), sep = "")
nH.mut = read.csv(nH.mut.fname, header = T)
rownames(nH.mut) = paste("mut", rownames(nH.mut), sep = "")
nH.medium = read.csv(nH.medium.fname, header = T)
rownames(nH.medium) = paste("mut", rownames(nH.medium), sep = "")

mode = seq(ncol(nH.medium))

# Prepare modeComparison
tnH.medium = as.data.frame(t(as.matrix(nH.medium)))
tnH.medium = cbind(data.frame("mode" = mode), tnH.medium)
modeComparison.medium = melt(tnH.medium, "mode", variable.name = "protein", value.name = "nH")
modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

tnH.mut = as.data.frame(t(as.matrix(nH.mut)))
tnH.mut = cbind(data.frame("mode" = mode), tnH.mut)
modeComparison.mut = melt(tnH.mut, "mode", variable.name = "protein", value.name = "nH")
modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

tnH.exp = as.data.frame(t(as.matrix(nH.exp)))
tnH.exp = cbind(data.frame("mode" = mode), tnH.exp)
modeComparison.exp = melt(tnH.exp, "mode", variable.name = "protein", value.name = "nH")
modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
modeComparison.exp <- na.omit(modeComparison.exp)
modeComparison.medium <- na.omit(modeComparison.medium)
modeComparison.mut <- na.omit(modeComparison.mut)

modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),                                                   data.frame("dataset" = "mut", modeComparison.mut),
                                    data.frame("dataset" = "medium", modeComparison.medium))

dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means
d = ddply(dat,c("dataset", "mode"), function(x) {
    mean.nH = mean(x$nH)
    data.frame(mean.nH)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")
```
### Dynamical divergence along normal modes

In this section we consider dynamical divergence using normal modes coordinates. We calculated <nH> and we normalized profiles.

```{r means}
# get means
mean.nH.exp =  subset(d, dataset == "exp")$mean.nH
mean.nH.mut = d.mut = subset(d, dataset == "no-selection")$mean.nH
mean.nH.medium = subset(d, dataset == "selection")$mean.nH
```

```{r comparison-of-means-100-modes}
# get first 100 modes and re-scale
mean.nH.exp = mean.nH.exp[1:100]
mean.nH.mut = mean.nH.mut[1:100]
mean.nH.medium = mean.nH.medium[1:100]

plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
points(mean.nH.mut, col = "green")
points(mean.nH.medium, col = "red")

@@

# plot comparative profiles 
plot(x = mean.nH.exp, 
     y = mean.nH.mut, 
     xlab = "<nH> experimental", 
     ylab = "<nH> no-selection")
abline(0, 1)

plot(x = mean.nH.exp, 
     y = mean.nH.medium, 
     xlab = "<nH> experimental", 
     ylab = "<nH> selection")
abline(0, 1)

plot(x = mean.nH.mut, 
     y = mean.nH.medium, 
     xlab = "<nH> no-selection", 
     ylab = "<nH> selection")
abline(0, 1)
```

### 2017-05-10 analysis-dynamical-nR.Rmd
charla 11-5-17

@@

plot(x = mean.nR.exp, 
     y = mean.nR.mut, 
     xlab = "<z.nR> experimental", 
     ylab = "<z.nR> no-selection")
abline(0, 1)

>>>>

plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
points(mean.nR.mut, col = "green")
points(mean.nR.medium, col = "red")

@@

plot(x = mean.nR.exp, 
     y = mean.nR.mut, 
     xlab = "<nR> experimental", 
     ylab = "<nR> no-selection")
abline(0, 1)

plot(x = mean.nR.exp, 
     y = mean.nR.medium, 
     xlab = "<nR> experimental", 
     ylab = "<nR> selection")
abline(0, 1)

plot(x = mean.nR.mut, 
     y = mean.nR.medium, 
     xlab = "<nR> no-selection", 
     ylab = "<nR> selection")
abline(0, 1)
```

### 2017-05-10 analysis-structure-core.Rmd
charla 11-5-17

To measure structural divergence we use z.RSD profiles, which are the best for most families.

The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors. We need to deal with this for quantitative analysis. Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*

@@

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(<z.RSD>)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
```

@@

```{r comparisons-between-profiles}

@@

if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.mut = mut.site.mut - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
}

# core n.sites

for (i in (1:n.sites)) {
  accept.mut.i = accept.mut[which(mut.site.mut == i)]
  p.accept.mut.i = mean(accept.mut.i)
  p.accept.mut[i] = p.accept.mut.i

@@

plot(x = p.accept.mut, y = CN, xlab = "log(paccept no-selection)")
plot(x = p.accept.mut, y = score, xlab = "log(paccept no-selection)")
plot(x = score, y = CN)

## calculate corelations
r.p.accept.mut.CN = cor(log(p.accept.mut), CN)
r.p.accept.mut.score = cor(log(p.accept.mut), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

plot(x = log(p.accept.medium.sel), y = CN, xlab = "log(paccept selection)")
plot(x = log(p.accept.medium.sel), y = score, xlab = "log(paccept selection)")
plot(x = score, y = CN)

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

>>>>

To measure structural divergence we use z.RSD profiles, which are the best for most families. The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)

@@

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD +  f95 * se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(<z.RSD>)") +
    coord_cartesian(ylim = c(-2, 3.5)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

knitr::kable(cor.df, digits = 2, caption = "Correlation between <z.RSD> profiles")
```

@@

```{r comparisons-between-profiles, fig.cap = "Yellow points are the active sites and green points are their contacts"}

@@

# correct indexes
if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.mut = mut.site.mut - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
  CN.CM = sim.data.mut$CN
  CN = c()

  for (i in (1:n.sites)) {
    CN[i] = CN.CM[which(mut.site.mut == i)][1]
  }
  CN = CN[indexes.core]
}

# core n.sites
for (i in (1:n.sites)) {
  accept.mut.i = accept.mut[which(mut.site.mut == i)]
  p.accept.mut.i = mean(accept.mut.i)
  p.accept.mut[i] = p.accept.mut.i

@@

plot(x = p.accept.mut, y = log(CN))
plot(x = p.accept.mut, y = score)
plot(x = score, y = log(CN))

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("comparison" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

plot(x = p.accept.medium.sel, y = log(CN))
plot(x = p.accept.medium.sel, y = score)
plot(x = score, y = log(CN))

## calculate corelations
r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("comparison" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

### 2017-05-10 analysis-structure-normal-modes.Rmd
charla 11-5-17

```{r prepare_site_data}
# prepare the data
Pn.exp = read.csv(Pn.exp.fname, header = T)
rownames(Pn.exp) = protein.exp
energy.exp = read.csv(energy.exp.fname, header = T)
rownames(energy.exp) = protein.exp

@@

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,2.5)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,1))

@@

### correlaction between mode profiles

>>>>

```{r prepare_site_data}
# prepare the data
Pn.exp = read.csv(Pn.exp.fname, header = T)
rownames(Pn.exp) = paste("exp", rownames(Pn.exp), sep = "")
energy.exp = read.csv(energy.exp.fname, header = T)
rownames(energy.exp) = paste("exp", rownames(energy.exp), sep = "")

@@

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,3)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,3))

@@

### correlaction between mode profiles
(calculated for the first 100 modes)

### 2017-05-10 analysis-structure.Rmd
charla 11-5-17

# add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

@@

To measure structural divergence we use z.RSD profiles, which are the best for most families.

The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors. We need to deal with this for quantitative analysis. Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*

@@

## find the active site and its contacts
active.sites = d$site[d$shell == 0]
contacts.active.sites = d$site[d$shell == 1]

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "<zRSDi>") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

```{r comparison-mean-z.RSD-vs-site}

# comparison of z.RSD profiles

ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
  geom_line() +
  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8) +
  labs(x = "site", y = "<zRSDi>") +
  geom_vline(xintercept = active.sites, show.legend = F) +
  geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) + 
  scale_colour_manual(name = NULL, values = myColors)

@@

plot(x = log(p.accept.mut), y = CN, xlab = "log(paccept no-selection)")
plot(x = log(p.accept.mut), y = score, xlab = "log(paccept no-selection)")
plot(x = score, y = CN)

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

plot(x = d.exp$mean.z.RSD, y = CN, xlab = "<zRSDi> experimental ")
plot(x = d.mut$mean.z.RSD, y = CN, xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = CN, xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

>>>>

# add pdb.info to site.info
site.info = cbind(site.info, pdb.info)

# find the active site and its contacts
active.sites = d$site[d$shell == 0]
contacts.active.sites = d$site[d$shell == 1]

```

@@

To measure structural divergence we use z.RSD profiles, which are the best for most families. The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean).

@@

print(active.sites)

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = c(active.sites), show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "<zRSDi>") +
    coord_cartesian(ylim = c(-2, 3.5)) + 
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

```{r comparison-mean-z.RSD-vs-site, fig.cap = "Yellow points are the active sites and green points are their contacts"}

# comparison of z.RSD profiles
ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
  geom_line() +
  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8) +
  labs(x = "site", y = "<zRSDi>") +
  geom_vline(xintercept = active.sites, show.legend = F) +
  geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +   
  coord_cartesian(ylim = c(-2,3.5)) +
  scale_colour_manual(name = NULL, values = myColors)

@@

plot(x = p.accept.mut, y = log(CN))
plot(x = p.accept.mut, y = score)
plot(x = score, y = log(CN))

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("comparison" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental ")
plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

### 2017-05-10 comparison_CA_CM.Rmd
charla 11-5-17

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison CA" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison CA" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison CM" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison CM" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)

# save data
CA.mean.exp = d.exp$median.Pn
CA.mean.mut = d.mut$median.Pn
CA.mean.medium = d.medium$median.Pn

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)

# save data
CM.mean.exp = d.exp$median.Pn
CM.mean.mut = d.mut$median.Pn
CM.mean.medium = d.medium$median.Pn

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)

# save data
CA.mean.exp = d.exp$mean.nH
CA.mean.mut = d.mut$mean.nH
CA.mean.medium = d.medium$mean.nH

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)

# save data
CM.mean.exp = d.exp$mean.nH
CM.mean.mut = d.mut$mean.nH
CM.mean.medium = d.medium$mean.nH

>>>>

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison CA" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison CA" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison CM" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison CM" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])

# save data
CA.mean.exp = d.exp$median.Pn[1:100]
CA.mean.mut = d.mut$median.Pn[1:100]
CA.mean.medium = d.medium$median.Pn[1:100]

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])

# save data
CM.mean.exp = d.exp$median.Pn[1:100]
CM.mean.mut = d.mut$median.Pn[1:100]
CM.mean.medium = d.medium$median.Pn[1:100]

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])

# save data
CA.mean.exp = d.exp$mean.nH[1:100]
CA.mean.mut = d.mut$mean.nH[1:100]
CA.mean.medium = d.medium$mean.nH[1:100]

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])

# save data
CM.mean.exp = d.exp$mean.nH[1:100]
CM.mean.mut = d.mut$mean.nH[1:100]
CM.mean.medium = d.medium$mean.nH[1:100]
